Separating Use and Reuse to Improve Both

### 2017-04-04 FACS/RelatedWork.tex
.

\section{Related Work}
The literature on code reuse is too vast to let us do justice of it in a fiew pages,
Our work is clearly inspired on Traits[sharly]; they are in turn insipired on module composition languages[]
and multiple inheritance[].

@@

Our close contendant is DeepFJig[]: all our gain over their model is based on our relaxation over abstract signatures.
Note how we solve the expression problem in the most radical way possible \marco{bruno, here you can insert some of the criticism over expression problem trivially and explain how is not applicable to us here.}

>>>>

\section{Related Work}
The literature on code reuse is too vast to let us do justice of it in a fiew pages,
Our work is clearly inspired on Traits~\cite{ducasse2006traits}; they are in turn insipired on module composition languages~\cite{ancona2002calculus}
and multiple inheritance~\cite{}.

@@

Our close contendant is DeepFJig~\cite{corradi2011deepfjig}: all our gain over their model is based on our relaxation over abstract signatures.
Note how we solve the expression problem in the most radical way possible \marco{bruno, here you can insert some of the criticism over expression problem trivially and explain how is not applicable to us here.}
